\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{fancyhdr}
\usepackage[margin=2.5cm]{geometry}

\usepackage{url}
\usepackage{makecell}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

\title{DUNE LCF White Paper}
\author{DUNE people}
\date{November 2024}


\begin{document}

%\end{abstract}

\maketitle
\abstract{
The Deep Underground Neutrino Experiment is going to do a lot of amazing things. It needs a lot of computing such as at the LCF machines. In this paper we briefly describe DUNE, its computing infrastructure, and summarize our use cases for LCF machines.}

\section{Introduction\label{sec:intro}}
A well-written introduction goes here.
\subsection{Introduction to DUNE\label{sub:duneintro}}
Briefly describe DUNE, its science goals, and the detectors at a high level. probably no more than one page is needed, perhaps two.
\subsection{DUNE software and computing \label{sub:dunesw}}
describe the current setup of software and computing, with primary focus on job submission, workflow management, data management, required services
\subsubsection{Job submission\label{sub:jobsub}}

\subsubsection{Workflow management\label{sub:workflow}}

\subsubsection{Data management\label{sub:dm}}

\subsubsection{Standard services\label{sub:services}}
List things like Rucio, metacat, databases, CVMFS


\section{Use cases involving GPUs\label{sec:gpu}}
Lots of cool things for which we need many GPUs
\subsection{ND}\label{sub:ND}
stuff
\subsection{FD accelerated components\label{sub:FD}}
more stuff

\section{Large-scale MPI processing needs\label{sec:mpi}}
talk about systematics variations and FC fits on large datasets

\section{other stuff\label{sec:other}}
whatever else we didn't talk about yet.
\subsection{Supernova burst processing\label{sub:sn}}
discuss rough CPU estimate, data sizes, focus on redundancy issues and ensuring we have multiple places to run in case of multiple outages at the time of an event.


\section{Conclusions}\label{sec:conc}
\end{document}
